---
title: '00- Collecting data from web'
author: 'Ali FRADY'
date: '02/12/2020'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Imports**

```{r include=FALSE}
source("Imports/00 - R dependencies.R")
source("Imports/00 - R dependencies.R")
source_python("Imports/00 - pyDependencies.py")
source_python("Imports/00 - scrapGoogle.py")
source_python("Imports/00 - scrapNewsAggregators.py")

```

## Building queries

**From gloassary **

https://businessfraudprevention.org/glossary-of-fraud-terms/


```{r queries, message=FALSE, include=FALSE, paged.print=FALSE}

Asset_misappropriation <- c(
'"Asset misappropriation"',
'"stealing receipts"',
'"stealing assets"',
'"disbursement fraud"'
)


Asset_Fraud<- c(
'"Asset Fraud"',
'"falsely recorded assets"',
'"falsely recorded revenue"',
'"Revenue Fraud"'
)

Understatement_of_Assets <- c(
  '"Understatement Revenues"', 
  '"Understatement Liabilities"'
)

Bid_rigging <- c(
  '"Bid rigging"',
'"collusive fraud"',
'"illegal contract" AND "competitive bidding"',
' "illegal contract without competitive bidding"'
)

billing_scheme <- c(
'"fraudulent payment to employee" ',
'"fraudulent payment" AND "employee"' 
)

Bribery <- c(
'"Bribery"',
'"soliciting value to influence act"',
'"bribe to influence act"',
'"Conflicts of Interest"',
'"Economic Extortion"',
'"Illegal Gratuities"'
)

Embezzlement <- c(
'"embezzlement of public funds"'
)

fictitious_expense <- c(
'"fictitious expense"',
'"fake receipts"',
'"novelty receipts"'
)

Fictitious_revenues <- c(
'"Fictitious revenues"',
'"false sale"'
)

Fraud_prevention <- c(
'"Fraud prevention"',
'deter fraud from occurring'
)

Financial_Statement_Fraud <-c(
  'Financial Statement Fraud',
'"financial misstatement"',
'"omitting facts" AND "financial statements"',
'"omitting facts financial statements"',
'"omitting disclosures"',
'"misstating amounts"',
'"misapplying GAAP"'
)

Front_Loading <- c('Front Loading')

ground_floor_opportunity <- c('ground floor opportunity',
                              'Tax haven')





Invoice_kickbacks <- c(
'Invoice kickbacks',
'overstated price"',
'illeagal gratuities'
)

Kiting_fraud <- c(
'"Kiting fraud"',
'conceal cash shortages'
)


occupational_fraud <- c(
 'occupational fraud and abuse'
)


Purchase_schemes <- c(
  "false invoicing"
)

fictitious_sales <- c(
'fictitious sales',
'altering sales receipts ',
'altering commission rates'
)

shell_company <- c(
'shell company',
'mirror an existing company',
'spelling deviation in the name of a company')

Segregation_duties <- c(
  'Segregation of duties'
)

Tax_fraud <- c(
'Tax fraud',
'excise tax',
'violating duty of income tax returns',
'cheat accounting calculations of net income'
)

Vendor_Fraud <- c(
'Vendor Fraud',
 'overcharge for purchased goods',
'shipment of inferior goods',
'non-shipment of paid goods'
)

White_collar_criminals <- c(
  'White-collar criminals'
)


Counterintelligence <- c(
  'Counterintelligence'
)


topic_name <- c(
  'Asset_misappropriation', 'Asset_Fraud', 'Understatement_of_Assets',
         'Bid_rigging', 'billing_scheme', 'Bribery', 'Embezzlement', 'fictitious_expense',
         'Fraud_prevention', 'Financial_Statement_Fraud', 'Front_Loading', 
         'ground_floor_opportunity',  
         'Invoice_kickbacks', 'Kiting_fraud', 'occupational_fraud', 'Purchase_schemes',
         'Purchase_schemes', 'fictitious_sales', 'shell_company', 'shell_company',
         'Segregation_duties', 'Tax_fraud', 'Vendor_Fraud', 'White_collar_criminals',
         'Counterintelligence'
)

```

**Aggregating queries/topics to model**
based on similarities, human interpretation and listing of most impacting events that happened in the last decades

```{r queries, message=FALSE, include=FALSE, paged.print=FALSE}

suspect <- c(
"extended confiscation",
"land confiscation",
"value confiscation",
"special confiscation",
"freeze of properties",
"prohibit transfer",
"prohibit movement of money",
"Shell company",
"Shell Bank",
#------------
"massive Siemens corruption scandal",
"'Sani Abacha' AND 'corruption'",
"'Najib Razak' AND 'Malaysia' AND 'shell companies'",
"'PDVSA' AND 'corruption'",
"'Mossack Fonseca' AND 'shell companies' AND 'Panama papers'",
"dodgy tourism deals in the Maldives",
"'troika dialog' AND 'tax havens'",
"'Andrej Babiš' AND 'Conflict of interest'"
)

Terrorism <- c(
  "commit terrorist acts",
  "'criminal activities' AND 'Business'",
  "Organized criminal group and  racketeering",
  "terrorist financing",
  "trafficking in human beings",
  "migrant smuggling",
  "sexual exploitation",
  "trafficking in narcotic drugs",
  "trafficking in psychotropic substances",
  "arms trafficking",
  "trafficking in stolen and other goods",
  "'kidnapping' AND 'business'",
  "illegal restraint and hostage-taking",
  #------
  "Blackwater mercenary",
  "Wagner mercenary",
  "Blackshield army",
  "D4S army"
)

financialCrime <- c(
  "counterfeiting currency",
  "counterfeiting and piracy of products",
  "environmental crime",
  "excise duties and taxes",
  "forgery",
  "insider trading and market manipulation",
  "forfeiture or confiscation determination",
  "tax crimes"
)


Fraud <- c("Asset misappropriation", "Asset Fraud", 'Understatement of Assets',
         'Bid rigging', 'billing scheme', 'Bribery', 'Embezzlement', 'fictitious expense',
         'Fraud prevention', 'Financial Statement Fraud', 'Front Loading', 
         'ground floor opportunity', 
         'Invoice kickbacks', 'Kiting fraud', 'occupational fraud', 'Purchase schemes',
         'Purchase schemes', 'fictitious sales',
         'Segregation duties', 'Tax fraud', 'Vendor Fraud', 'White collar criminals',
         'Counterintelligence',
         #------
         "'Alberto Fujimori' AND 'Embezzlement' AND 'public relations'",
         "'Chechnya' AND 'bribe' AND 'job'",
         "'monopoly' AND 'corruption' AND 'ruling family'",
         "'President Ricardo Martinelli' AND 'embezzlement'",
         "'The Russian Laundromat'",
         "'Correa' AND 'Mariano Rajoy' AND 'illicit'",
         "'Gupta family' AND 'corruption'", 
         "' Petrobras and Odebrecht' AND 'lava jato'"
)

topic_name <- c(
 "suspect", "Terrorism", "financialCrime", "Fraud"
)
```

## Generate pagination links for google news

```{r}
req_GOOG(query = "extended confiscation", pages = seq(from = 0, to = 190, by = 10))
```
## Getting articles' links from google news researching

```{r}
Articles_by_topic(query = "extended confiscation", pages = seq(from = 0, to = 10, by = 10))
```
## Store scrapped information:
into a dataframe that collects the query, the source link, the title, the body and keywords 
```{r}
get_news(query = "extended confiscation", pages = seq(from = 10, to = 20, by = 10))
```

## Loop over all queries/topics and save to local storage

```{r}
max_pagination = 5
for (name in topic_name) {
  reqGOOG <-c(get(name))
  pb <- winProgressBar(title = paste0("Googling for ", name), min = 0,max = length(reqGOOG), width = 700)
  df <- data.frame()
  i<-1
  for (k in reqGOOG) {
    for (j in 0:(max_pagination-1)) {
      setWinProgressBar(pb, i, title=paste0('Topic: ', name, ' Query: ',k,' Pagination: ', j+1 ))
      try(
        df <- df %>%
          rbind(
            as.data.frame(
              get_news(query = k, pages = seq(from =  j, to = (j*10)+10, by= 10))
              )
            )
        )
    }
    i <- i+1
    print("sleeping...")
    Sys.sleep(sample(1:5,1))
  }
  close(pb)
  saveRDS(df,paste0('data/',name,as.character(Sys.Date()),".rds") )
  print(paste("saved",name,as.character(Sys.Date()),".rds"))
  
}
```

## Preview of dataset we collected

```{r}
df %>%
  tibble() %>%
  head()
```





